Maenpuen et al.~Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-04-07 ms/LMA_method.Rmd
udpate make

---
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    toc: FALSE
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_args:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

@@

Phisamai Maenpuen^1,2,3^,
Masatoshi Katabuchi^1,\*^,
Yusuke Onoda^4^,
Cong Zhou^1,2^,
Jiao-Lin Zhang^1,3\*^,
Ya-Jun Chen^1,3,5^

@@

![](../figs/LMA_sp_gr.png)

@@

![](../figs/LMA_ind_gr.png)

@@

![](../figs/fig_cv.png)

>>>>

---
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{lineno}
  - \linenumbers
output:
  html_document:
    toc: FALSE
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: no
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    pandoc_arg:
      - "--filter"
      - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

@@

Phisamai Maenpuen^1,2,3^,
Masatoshi Katabuchi^1\*^,
Yusuke Onoda^4^,
Cong Zhou^1,2^,
Jiao-Lin Zhang^1,3\*^,
Ya-Jun Chen^1,3,5^

@@

![](../figs/lalt_pool_grid.png)

@@

![](../figs/lalt_tree_grid.png)

@@

![](../figs/cv_pool.png)
